\begin{recipe}{Chocolate-Covered Cherry Cookies}{Makes 48 cookies}{1 hour}
  \ingredient[1\nicefrac{1}{2}]{cups}{flour}
  \ingredient[\nicefrac{1}{2}]{cup}{unsweetened cocoa powder}
  \ingredient[\nicefrac{1}{4}]{tsp.}{salt}
  \ingredient[\nicefrac{1}{4}]{tsp.}{baking powder}
  \ingredient[\nicefrac{1}{4}]{tsp.}{baking soda}
  Combine and set aside.
  \ingredient[1]{10oz. jar (48)}{ maraschino cherries}
  Drain and set aside.  Reserve the juice.
  \ingredient[\nicefrac{1}{2}]{cup}{butter}
  \ingredient[1]{cup}{sugar}
  \ingredient[1]{}{egg}
  \ingredient[1\nicefrac{1}{2}]{tsp.}{vanilla extract}
  In a large mixing bowl, beat butter on medium speed for 30 seconds.  Add sugar and beat until fluffy.  Add egg and vanilla.  Beat well.  Gradually add dry ingredients.  Beat until combined.  Shape into 1 inch balls.  Place 2 inches apart on ungreased cookie sheet.  Press down center of each ball with thumb.  Place a drained cherry in the center of each cookie.
  \ingredient[1]{6oz. package}{semisweet chocolate pieces (not imitation)}
  \ingredient[\nicefrac{1}{2}]{cup}{sweetened condensed milk}
  For frosting, in a small saucepan combine chocolate pieces and sweetened condensed milk.  Cook and stir over low heat until chocolate is melted.  Stir in 4tsp of reserved cherry juice.  Spoon 1tsp of frosting over each cherry, spreading to cover cherry.  (Frosting may be thinned wih additional cherry juice if needed.)
  Bake in 350\0F oven for 10 minutes or until edges are firm.  Remove 
  from oven and cool on wire rack.
\end{recipe}